Centrality and Activity for Envolving Networks

### 2013-06-24 network-science/paper.tex

The clustering coefficient\cite{newman2010networks}, namely
\begin{equation}
c.c=\frac{\#\text{closed paths of len 2}}{\#\text{paths of len 2}},
\end{equation}
for a typical social network is a possitive
number, which means people are more willing to make interactions with close
related people than unfamiliars.

>>>>

The clustering coefficient\cite{newman2010networks}, namely
\begin{equation}
c.c=\frac{\#\text{closed paths of length 2}}{\#\text{paths of length 2}},
\end{equation}
for a typical social network is a positive number, which means people are more
willing to make interactions with close related people than unfamiliar ones.
